---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# dontpanic

The goal of dontpanic is to be the coding equivalent of a towel. My helper functions are parked here. Work in progress, use at own risk.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

## Signifiers

I'll bet I'm trying to reinvent the wheel here, there's probably a mountain of literature on how to track projects using emoji on github. 

But right now I've got less than two weeks to prepare for a talk on visualisation to people who are very smart. (I also really like them and want them to be my friends, and if I take on too much right now I'll be too wild-eyed crazy to be approachable.)

So, I'm just going to dive in and make something up to get me through the next few weeks.  

### Structure

I want to run my eyes down commit history and have things pop out. 

You're usually looking for an issue not a person, so the issue should be on the lefthand side. The next question might be who made that change. So, signifier for person goes at the end. 

> :issue_emoji: Some commit message. :person_emoji:

### Signifiers

- `pandagrrl` :notes:. 
- :musical_score: Documentation.
- :musical_keyboard: Updated README.Rmd. Quavers indicate daily, weekly, and future logs in my bullet journal.
- :cat: Any work on functions.

